### 2019-02-05 thesis_report/methods.tex
SJL introduced

		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker_universal_1991,sticlet_robustness_2017}.
		The short junction limit is valid for $W<\xi$, where $\xi$ is the superconducting coherence length.
		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.

>>>>

		We derive the spectrum by calculating the scattering matrix $S(\epsilon)$ for the normal region and applying the Andreev bound state condition (Eq.~\eqref{eq:bound_state_condition_sjl}) for the short junction limit \cite{beenakker_universal_1991,sticlet_robustness_2017}.
		The short junction limit corresponds to the case where we can neglect the energy dependence of the scattering matrix: $S(\epsilon) \approx S(0)$.
		This limit is valid for $W<\xi$, where $\xi$ is the superconducting coherence length.
		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
